---
title: "EDFR Interview Questions"
author: "Oswaldo Felix"
date: "4/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
library(tidyverse)
```

## Problem 1

In each box of Cerebral Cereal, there is a plastic figurine portraying a well-known philospher. If there are n different philosphers, how many boxes would you have to buy on average to get a complete set?

```{r}
# Initialize variables and matricies
runs <- 1000
n <- 273
s <- (n/2)*(1 + n)
purchased <- 0
results <- vector('numeric', length = runs)

# Model
for (i in 1:runs){
  purchased <- 0 # reset 
  phil <- vector('numeric', length = runs) # reset
  while (sum(unique(phil)) < s){ # check if unique sequence 1:n exists
    purchased <- purchased + 1 # counter
    p <- sample(1:n, 1) # equal random chance
    phil[purchased] <- p # store seed
   }
  results[i] <- purchased
}
 
avg = mean(results)
```

In this particular set of runs, the experimental average was `r round(avg)`. The higher the number of simulations the closer the experimental value converges to the theoretical value. At 10,000 runs the numbers converged around 314.

## Problem 2

The 190 students in a course attend either the first or second hour of a seminar. When the choice was left to each student, only 85 students turned up the first hour and 105 the second hour. May we draw the conclusion that the second hour is more popular? Is the difference significant on the 95% level? On the 99% level? Formulate null hypothesis and test it in a simulation program.

Null hypothesis: There is no preference in student choice among seminar classes

```{r}
# Initialize variables and matricies
runs <- 1000
n <- 190
results_1 <- vector('numeric', length = runs)
results_2 <- vector('numeric', length = runs)

# Model
for (i in 1:runs){
  count <- 0 # reset 
  students <- vector('numeric', length = 190) # reset
  while (count < n){ # continue until all students have chosen
    count <- count + 1 # add one to count
    choice <- sample(c(1,2), 1) # choose first or second room
    students[count] <- choice # store prize
   }
  students <- as.data.frame(students) # change to data frame for functions
  first <- students %>% 
    filter(students == 1) %>% 
    nrow() # counts number of students
  second <- students %>% 
    filter(students == 2) %>% 
    nrow() # counts number of students
  results_1[i] <- first
  results_2[i] <- second
}

# Finalizing results dataframe
results_f <- data.frame(results_1, results_2) %>% 
  mutate(prop = results_1/results_2)

# Running t-test
sample <- results_f$prop
null <- c(rep(1, runs))
my_ttest <- t.test(sample, null)
my_ttest # not significantly different
```

This is as far as I got with the second problem before running out of time. 
These were fun to solve!